Notes on the low density parameters in {\tt MAESTRO}

### 2009-06-08 docs/lo_density/lo_density.tex
added a cute figure about the cutoff density and coordinate

At several points in the algorithm, we compute {\tt anelastic\_cutoff\_coord}, 
{\tt base\_cutoff\_density\_coord}, and {\tt burning\_cutoff\_density\_coord} by 
setting the corresponding coordinate equal to $r$ as soon as $\rho_0(r)$ is less than 
or equal to that particular cutoff value.  We compute the cutoff coordinate at the
coarsest level, and then set the coordinate at the next finer level to be twice that
of the coarser level.  We set the coordinates at the following points in the code:

>>>>

At several points in the algorithm, we compute {\tt anelastic\_cutoff\_coord}, 
{\tt base\_cutoff\_density\_coord}, and {\tt burning\_cutoff\_density\_coord} by 
setting the corresponding coordinate equal to $r$ as soon as $\rho_0(r)$ is less than 
or equal to that particular cutoff value (see Figure \ref{Fig:Cutoff}.
We compute the cutoff coordinate at the
coarsest level, and then set the coordinate at the next finer level to be twice that
of the coarser level.  We set the coordinates at the following points in the code:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[hpb]
\centering
\includegraphics[width=4.0in]{\lodensfigpath/cutoff}\hspace{0.2in}
\begin{minipage}[b]{5.0in}
\caption{Image of how the cutoff density and cutoff coordinates
are related.\vspace{2em}}
\end{minipage}
\label{Fig:Cutoff}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
